SSA based global code motion of identical computations

### 2017-04-15 acmart-pacmpl-template.tex
contrib

The main contributions of this paper are:
\begin{itemize}
\item a new optimistic algorithm to move computations out of branches,
\item cost models to reduce live-range and reduce spills,
\item a technique to maximize hoisting in an optimistic approach by partitioning
  the list of potential candidates sorted by their DFS visit number,
\item performance evaluation of the implementation in \LLVM{}.
\end{itemize}

@@

Rosen \cite{rosen1988global} explain moving computations from successors. Their
algorithm iterates on computations of same rank and move the code with identical
computations from the sibling branch to a common dominator.

@@

>>>>

The main contributions of this paper are:
\begin{itemize}
\item a new optimistic algorithm to move computations out of branches,
\item a cost model to reduce interference and reduce spills,
\item a technique to maximize hoisting in an optimistic approach by partitioning
  the list of potential candidates sorted by their DFS visit number,
\item experimental evaluation of our implementation in \LLVM{} which combines
  SSA based liveness analysis, and ranking of expressions to move very busy
  expressions in order to reduce code-size (and improve performance in some
  cases).
\end{itemize}

@@

@@

Rosen \cite{rosen1988global} also introduced moving computations from successors
using value numbering. Their algorithm iterates on computations of same rank and
move the code with identical computations from the sibling branch to a common
dominator if they are very busy \cite{steven1997advanced}.
